Exploring and Reverse Engineering the Motives Behind API Modifications

### 2015-03-27 rmtw/a6/latex8.tex
sdf

\section{Existing Literature}
This section will introduce the topics of API design andsoftware evolution, and provide a review of literature which is directly related to our study.

@@

Software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1. The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs. Our ability to correctly predict the motives compared to the actual motives of the architects which were made clear during the interviews, will serve as the basis for answering RQ2.

>>>>

\section{Existing Literature}
This section will introduce the topics of API design and software evolution, and provide a review of literature which is directly related to our study.

@@

The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1. The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs. Our ability to correctly predict the motives compared to the actual motives of the architects which were made clear during the interviews, will serve as the basis for answering RQ2.
